---
documentclass: article
classoption: [a4paper,11pt,twocolumn]
subparagraph: yes
header-includes:
   - \usepackage[latin1]{inputenc}
   - \usepackage[T1]{fontenc}
   - \usepackage[leqno,fleqn]{amsmath}
output:
  pdf_document:
    highlight: zenburn
    includes:
      before_body: includes/tex/doc_prefix.tex
      in_header: includes/tex/header.tex
    keep_tex: yes
    number_sections: yes
bibliography: includes/bib/icphs2019.bib
---

```{r, 'setup', include=FALSE}
library(knitr)
f <- function(x, options) {
  lab <- paste0(options$fig.lp, options$label)
  paste(
        "\\begin{figure}[!h]\n\\caption{", options$fig.cap.top, "}\\label{", lab,"}\n", 
        hook_plot_tex(x, options), 
        "\\end{figure}\n\n", sep = "")
}
knit_hooks$set(plot = f)
```

\section{Introduction}

The following rules apply to all submitted papers:

\begin{itemize}
  \item they must be written in English
  \item they must not contain the name(s) of the author(s) (for anonymous 
  review)
  \item the maximum is four pages for Congress papers, plus up to one 
  additional page of references. Papers for Plenary lectures can be longer
  \item they must be submitted in PDF format (cf. Section 4)
  \item the paper submission will occur via a web interface
\end{itemize}

This paper template can be found on the conference website. If there are 
special questions or wishes regarding paper preparation and submission for 
ICPhS 2019, correspondence should be addressed to icphs2019@arinex.com.au. 
Information for full paper submission will be available on the web at 
\url{http://www.icphs2019.org/}.



\section{Page layout and style}

The page layout should conform to the following rules. By far the easiest way 
to meet these requirements is to use the supplied templates and check details 
against this example file. If for some reason you cannot use the template, 
please follow these rules as carefully as possible, or contact the editors at 
icphs2019@arinex.com.au for further instructions.


\subsection{Basic layout features}

\begin{itemize}
  \item The layout is appropriate for A4 format.
  \item Two columns are used except for the title part and possibly for large 
  figures that need a full page width.
  \item Left margin is 20 mm. Right margin will depend on the size of the 
  paper. Column width is 80 mm.
  \item Spacing between columns is 10 mm.
  \item Top margin 25 mm (except first page which has 30 mm to the title top). 
  Bottom margin will depend on the size of the paper.
  \item Text height (without headers and footers) is a maximum of 235 mm. 
  Headers and footers should be left empty.
  \item Check indentations and spacings by comparing with this example file.
\end{itemize}


\subsubsection{Headings}

Section headings are centered in boldface with capitalized letters. 
Sub-headings start at the left margin in the column with the first letter 
capitalized and the rest of the heading in lower case. Sub-sub-headings appear 
like sub-headings, except that they are in italics and not boldface. See 
examples in this file. No more than 3 levels of headings should be used. Empty 
lines should be left above and below each section heading.


\subsection{Text font}

Times or Times New Roman font is used for the main text. Recommended font 
size is 11 points. Other font types may be used if needed for special 
purposes. If using any non-Unicode fonts, these must be embedded in the final 
PDF file.

The \LaTeX template can be used either with plain \LaTeX or \XeLaTeX.


\subsection{Figures}

All figures should be centered on the column (or page, if the figure spans 
both columns). Figure captions should precede each figure and have the format 
given in Fig. \ref{fig:vowels}.

Figures should preferably be line drawings. If they contain grey shades or 
colours, it should be checked that they print well on a high-quality noncolour 
laser printer.

\begin{figure}[!ht]
  \caption{The vowel chart used in the International Phonetic Alphabet (IPA).}
  \label{fig:vowels}
  \begin{center}
  \includegraphics[width=6cm]{./includes/figures/ipa.eps}
  \end{center}
\end{figure}


\subsection{Tables}

An example of a table is shown as Table \ref{tab:decibel}. Somewhat different 
styles are allowed according to the type and purpose of the table. Colour 
should not be used, but grey shading is allowed. There should be a margin of 
6 points (pt) above and below the table.

The caption text may be above or below the table, but this should be 
consistent throughout the submission. Left and right indentation of the 
caption should be 0.5 cm.

\begin{table}[!ht]
  \caption{This is an example of a table showing Decibel (dB) ratios.}
  \label{tab:decibel}
  \begin{center}
  \begin{tabular}{|c|c|}
  \hline
  \rowcolor[gray]{.75}
  ratio    & Decibels \\
  \hline
  $1/1$    & $0$      \\
  $2/1$    & $6$      \\
  $3.16$   & $10$     \\
  $1/10$   & $-20$    \\
  $10/1$   & $20$     \\
  $100/1$  & $40$     \\
  $1000/1$ & $60$     \\
  \hline
  \end{tabular}
  \end{center}
\end{table}


\subsection{Equations}

Equations should be placed on separate lines and numbered. An example of an 
equation is given below:
\begin{equation}\label{eq:tzero}
  t_0 = \frac{1}{f_0}
\end{equation}
\noindent Numbers of equations can be on the right or on the left margin of the 
text column.


\subsection{Examples}

Examples from other languages can either be presented in the body text, or, 
if referred to elsewhere or particularly long and complex, can be put on a 
separate, numbered line, as should be done for equations.


\subsection{Phonetic fonts}

We recommend that you use Unicode IPA phonetic symbols. For information about 
how to access Unicode fonts, see \cite{IPA-SIL} or \cite{IPA-KEYBOARD}. If 
you do not use Unicode symbols, the font you use must be embedded. Please 
remember to check this,  e.g. by inspecting the "Document Properties --- 
Fonts" in Acrobat Reader. Or you can use `TIPA`: \textipa{/Sip/-/SIp/}


\subsection{Page numbering}

Page numbers will be added electronically to the document later. 
\textit{Please do not add page numbers and please do not make any footers or 
headers!}


\subsection{References}

Please use just the reference number in square brackets. Formulations with 
author names like "\ldots\ as Ladefoged \cite{Ladefoged:2003} showed that 
\ldots" are acceptable but not "as shown in [Ladefoged, 3]" or "as shown in 
(Ladefoged [3])".

References are to be numbered in alphabetical order. Please double-check the 
final version of your paper with regard to the correct correspondence of 
references to their numbers.


\subsection{Hyperlinks}

Links to URLs or email addresses should be formatted as normal text, 
\textit{not} as hyperlinks and not blue or underlined etc. Usually hyperlinks 
to web pages are listed in the references section. If required, line breaks 
can be placed within URLs after slashes or dashes 
(cf. \cite{IPA-SIL, IPA-KEYBOARD}), but doublecheck that no hyphens are 
inserted.


\subsection{Footnotes and endnotes}

If footnotes cannot be avoided they should appear as endnotes.\footnote{This 
footnote appears here as an endnote and could be avoided in this case.}



\section{Multimedia files}

Multimedia data that are part of the paper are to be embedded in the submitted 
PDF; they cannot be submitted as supplementary data. Any images are to be 
included in the paper as Figures (see Section 2.3 above). It is the authors' 
responsibility to check image quality ahead of submission. Audio examples are 
to be embedded within the PDF. To do this, authors can generate the PDF, and 
then embed the audio files using Adobe Acrobat Professional. Alternatively, 
they may use other software that offers the same outcome, so that the audio 
is included in the PDF. The presence of audio data should be identified in 
the text.

We encourage authors to illustrate video data using still photographs from 
the video, and to include them as figures in the PDF. We cannot accept 
embedded video files, but authors are welcome to refer readers to a URL on 
the internet where these can be viewed.



\section{PDF details}

PDF files submitted must comply with the following requirements:

\begin{enumerate}
  \item all special fonts and symbols must be embedded in the PDF file so 
  that correct rendering of the PDF does not depend on the fonts installed 
  on the viewer's computer
  \item there must be no password protection on the PDF file, i.e. PDF files 
  must not be protected by PDF security in any way, i.e. content extraction, 
  document assembly, high resolution printing etc. must not be forbidden
  \item PDF files should not contain any colours, hyperlinks, multimedia or 
  3D content, and no JavaScript or forms
  \item PDF files should be no larger than 5 Mb.
\end{enumerate}



\section{Anonymity}

In ICPhS 2019 submissions, an anonymous reviewing process will be used. This 
means that for the first submission the name(s) of the author(s) and their 
affiliation(s) \emph{must not} be mentioned. In addition, please refrain from 
using acknowledgements. Please also try to make your own previous research as 
anonymous as possible. As an example: do not write "In our previous study [7] 
we could show\ldots" but "As shown in [7]\ldots". Or refer to your own 
published or otherwise widely known work, and to that of the other authors, 
in the "Julius Caesar style", i.e. in the third person (for example: his 
work, her work, their work). Reference as "anonymous" only work that you or 
the other authors have submitted for publication, but which has not yet been 
published, e.g. [8].

Please make sure that no author details appear in the Document Properties of 
the PDF file. \emph{For the revised paper submission author details are of 
course needed}. Acknowledgements and references to one's own work are 
possible as usual.




\section{Format of references}

Monographs such as \cite{Fant:1960} consist of author(s) last name(s), 
initial of the first name(s), year of publication, the title in italics, 
location of the publication, publisher. Please use the punctuation signs for 
structuring as presented in \cite{Fant:1960}.

The names of multiple authors are separated only by commas and they are 
always listed in the sequence last name, comma, initial(s) of the first 
name(s) (cf. the examples \cite{Beattie/etal:1982} and 
\cite{Peterson/Barney:1952}). Ampersands "&" and "and" are not needed.

Contributions to volumes, e.g. \cite{Stevens:1999}, follow the convention 
that the title of the volume is in italics, but not the title of the 
contribution. The book editors appear before the book title. The page numbers 
are at the end.

Journal articles should be handled in the same way as contributions to 
volumes except that the title of the journal is in italics and that the 
editors are not listed. Longer names of well-known journals can be 
abbreviated, e.g. \cite{Peterson/Barney:1952}. Articles in conference 
proceedings such as \cite{Ladefoged:2003} are referenced in the same way as 
journal articles. The word \textit{proceedings} can be abbreviated and the 
location should be mentioned after the name of the conference. Here, 
abbreviations of well-known conferences are possible.



\section{R scripts}

You can use knitr code chunks like in any .Rmd document: 

```{r, 'chunk_ex'}
2 + 2
```

This includes inline code: 2 + 2 = `r 2 + 2`. 

R scripts can be loaded as well: 

```{r, 'load_script', echo=TRUE, message=FALSE, warning=FALSE}
source("./includes/scripts/analysis.R")
```

Which means you have access to any objects assigned in the script, like Figure 
\ref{fig:ex_plot}: 

```{r, 'ex_plot', fig.align='center', fig.width=2.75, fig.height=1.5, fig.cap.top="This is a figure caption.", fig.pos='h', fig.lp='fig:'} 
cars_plot
```


\bibliographystyle{./includes/bib/icphs2019.bst}
\bibliography{./includes/bib/icphs2019.bib}

\theendnotes

